---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# kim

<!-- badges: start -->
[![R build status](https://github.com/jinkim3/kim/workflows/R-CMD-check/badge.svg)](https://github.com/jinkim3/kim/actions)
[![Travis build status](https://travis-ci.com/jinkim3/kim.svg?branch=master)](https://travis-ci.com/jinkim3/kim)
<!-- badges: end -->

This package facilitates and simplifies analyses of experimental data. 
Examples of functions include a function that plots sample means of groups 
in a factorial experimental design, a function that conducts robust 
regressions with bootstrapped samples, and a function that conducts 
mediation analyses.

## Installation

You can install the released version of kim 
from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("kim")
```

You can also install the development version from
[GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("jinkim3/kim")
```

## Example

Here are some examples of using this package.

```{r example, eval = FALSE}
library(kim)

# plot sample means of groups in a factorial experimental design
plot_group_means(data = mtcars, dv_name = "mpg", iv_name = "gear")

# conduct a robust regression with bootstrapped samples
robust_regression(data = mtcars, formula = mpg ~ cyl * hp)

# conduct a regular multiple regression
multiple_regression(data = mtcars, formula = mpg ~ gear * cyl)

# conduct a mediation analysis
mediation_analysis(data = mtcars, iv_name = "cyl", mediator_name = "disp", dv_name = "mpg")
```
